### 2020-04-07 draft.tex
new thing

We want to show that for any $f\colon D\to D'$ the square
\begin{equation}\label{eqn.cart1}
\begin{tikzcd}
	D(1)\ar[r, "f_1"]\ar[d, "\pi"']&
	D'(1)\ar[d, "\pi'"]\\
	D(0)\ar[r, "f_0"']&
	D'(0)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$ iff for all functions $g\colon X\to X'$, the naturality square
\begin{equation}\label{eqn.cart2}
\begin{tikzcd}
  D(X')\ar[r, "f_{X'}"]\ar[d, "D(g)"']&
  D'(X')\ar[d, "D'(g)"]\\
  D(X)\ar[r, "f_X"']&
  D'(X)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$. We will freely use the natural isomorphism
$D(X)\cong\Set^{\down}(!_X, D!_0)$ from
\ref{prop:set.characterizing.extent}, which allows us to identify Diagram
\ref{eqn.cart2} with
\begin{equation}\label{eqn.cart3}
\begin{tikzcd}
 \Set^{\down}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Set^{\down}(!_{X'}, D'!_0)
  \ar[d, "!_{g}^{\ast}"]\\
  \Set^{\down}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
 \Set^{\down}(!_X, D'!_0) 
\end{tikzcd}
\end{equation}

@@

\begin{thm}\label{thm:set.poly.cart.equiv.dir.cart}
  There is an equivalence of categories
  $$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
  between the category of polynomial functors and cartesian transformations and
  Dirichlet functors and cartesian transformations. This equivlalence sends
  representables to representables
  $$(-)^N \mapsto N^{(-)}.$$
\end{thm}
\begin{proof}
TODO
\end{proof}

\begin{cor}
  Let $D$ be a Dirichlet functor. Then the category
  $\Dir_{/_{\ulcorner} D}$
  of Dirichlet functors with a cartesian map to $D$ is a topos.
\end{cor}
\begin{proof}
By Theorem \ref{thm:set.poly.cart.equiv.dir.cart}, this category is equivalent
to $\type{Poly}_{/_{\ulcorner} P}$ for a polynomial $P$. But this is a topos as
observed in Remark 2.6.2 of \cite{GHK:Analytic.Monads}.
\end{proof}
\dis{How does this topos compare to the topos $\Dir_{/D}$?}
\jaz{The following story: it generalizes to $\infty$-categories, which is why
  I'm writing it this way.}

\begin{defn}
A \emph{modality} on a category $\Ca$ is a stable orthogonal factorization
system $(\La, \Ra)$. \jaz{see Anel Biederman Finster Joyal \cite{ABFJ:Blakers.Massey}}

A modality is \emph{lex} if for any square
\[
  % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAEEQBfU9TXfIRRkAjFVqMWbAELdeIDNjwEiI8uPrNWiEAGE5fJYNWkx1TVJ0ARbuJhQA5vCKgAZgCcIAWyRkQOCCQAJnNJbRBXAwjPH0QQ-0DEAGZQrTYHKI9vX2oApDUQBjoAIxgGAAV+ZSEQdywHAAscEFTLEAbMmPzcxJSJNJ0AaxbCkrLKoxUdOsbmrgouIA
\begin{tikzcd}
A \arrow[r, "h"] \arrow[d, "g"'] & C \arrow[d, "f"] \\
B \arrow[r, "k"']                & D               
\end{tikzcd}
\]
where $f$ and $g$ are in $\La$ and $h$ and $k$ are in $\Ra$ is a pullback. (See
Theorem 3.11 of \cite{RSS:Modalties.in.HoTT}, condition (vii).)

We say that a modality $(\La, \Ra)$ is \emph{contained in} $(\La', \Ra')$ ---
written $(\La, \Ra) \leq (\La', \Ra')$ --- if $\Ra \subseteq \Ra'$.
\end{defn}

\begin{prop}
If $(\La, \Ra)$ is a modality on $\Ca$, then there is an induced modality $(\La_X,
\Ra_X)$ on $\Ca_{/X}$ \jaz{I'll flesh this out in a bit, see
  \cite{ABFJ:Blakers.Massey}}. If $(\La, \Ra)$ is lex, then so is $(\La_X, \Ra_X)$.
\end{prop}

\begin{prop}
There is an equivalence between the order of lex modalities on a topos and the
order of subtoposes.
\end{prop}
\begin{proof}
Idea: we take those objects whose terminal morphism is in $\Ra$.
\end{proof}

\begin{prop}
The orthogonal factorization system $(\term{vertical}, \term{cartesian})$ on
$\Set^{\downarrow}$ (given by the cartesian fibration $\Set\op \to \Set$) is a
lex modality.
\end{prop}

\begin{thm}
The left exact modality $(\term{vertical}_D, \term{cartesian}_D)$ on
$\Set^{\downarrow}_{/\pi}$ exhibits $\Set^{\downarrow}_{/_{\ulcorner} \pi}$ as a
subtopos.

As a corollary, we have a subtopos inclusion $\Dir_{/_{\ulcorner} D}
\hookrightarrow \Dir_{/D}$. \jaz{So $\Dir_{/D}$ is equivalently a presheaf topos
  $\Set^{\downarrow/D}$; what is the topology that presents $\Dir_{/_{\ulcorner}
  D}$ as a sheaf topos?}
\end{thm}

\section{Dirichlet Functors on Homotopy Types} \label{sec:type.level}

\begin{prop}
  There is an adjoint quintuple:
  \[
    \begin{tikzcd}
      \Ha \arrow[r, "\const"] \arrow[r, leftarrow, shift left = 5,
      "\term{cod}"] \arrow[r, leftarrow, shift right = 5, "\term{dom}"]
      \arrow[r, shift left = 10, "!^{(-)}"]  \arrow[r, shift right = 10, "!_{(-)}"] & \Ha^{\down}
    \end{tikzcd}
  \]
  All three functors $\Ha \to \Ha^{\down}$ are fully faithful.
\end{prop}
\begin{proof}
There is an adjoint triple $\begin{tikzcd} \ast \arrow[r,leftarrow] \arrow[r,
  bend left] \arrow[r, bend right] & \down \end{tikzcd}$. The middle three
functors are given by restricting along this adjoint triple; the outer two are
given by Kan extending. By Lemma \ref{lem:kan.extending.cone.adds.initial}, we
may calculate these as
  $$X \mapsto \begin{tikzcd} 0 \arrow[d, "!^X"] \\ X \end{tikzcd}
  \qquad\text{and}\qquad
  X \mapsto \begin{tikzcd} X \arrow[d, "!_X"] \\ \ast \end{tikzcd}$$
It is easy to see that the unit $X \to \term{dom} !_{X}$ is an equivalence (it is in
fact an identity), so $!_{(-)}$ is fully faithful. Therefore, all the functors
going from $\Ha \to \Ha^{\down}$ are fully faithful.
\end{proof}

\begin{prop}\label{lem:bang.preserves.weakly.contractible.colimits}
  The functor $!_{(-)}$ preserves weakly contractible colimits.
\end{prop}
\begin{proof}
  To see that $!_{(-)}$ preserves weakly contractible colimits, recall that colimits in $H^{\down}$ are calculated pointwise. It remains to show, then, that the map
  \[
    \begin{tikzcd}
    \colim S_i \arrow[r, equals] \arrow[d] & \colim S_i \arrow[d] \\
    \colim \ast \arrow[r] & \ast 
    \end{tikzcd}
  \]
  is an equivalence in $H^{\down}$, for which it suffices to show that $\colim \ast$ is contractible. But the colimit of the terminal diagram is the (Kan-fibrant replacement of) its indexing simplicial set -- since we assumed the diagram was weakly contractible, $\colim \ast$ is contractible.
\end{proof}

Now we will define the \emph{extent} of a bundle, the Dirichlet functor it
corresponds to. This sends a bundle
$\pi : E \to B$ to the functor
$$X \mapsto \sum_{b : B} E_b^X.$$
We will, however, give a more abstract definition of the extent, and then
calculate a number of presentations of it.

\begin{defn}
Consider the functor $!_0 : \down \to \Ha\op$ picking out the unique morphism $1\to 0$ in $\Ha\op$. Sending a functor $\Ha\op\to\Ha$ to its precomposition with $!_0$ gives an evaluation functor
  $$\Ha^{\down} \xleftarrow{\ev_{!_0}} \Fun(\Ha\op, \Ha).$$
  This functor admits a right adjoint by right Kan extension; we define the
  \emph{Dirichlet extent} functor $\ext : \Ha^{\down} \to \Fun(\Ha\op,
  \Ha)$ to be this right adjoint:
  $$\ext_{\pi} :\equiv \term{ran}_{!_0} \pi.$$
\end{defn}

\begin{prop}
  The functor $\ext$ is fully faithful, giving an equivalence 
  $$\Ha^{\down} \simeq \Dir$$
  where $\Dir$ is the category of Dirichlet functors and natural transformations.\dis{What is $\Dir$; have we defined Dirichlet functors in this context?}
\end{prop}
\begin{proof}
Since $!_0 : \down \to \Ha\op$ is fully faithful, the counit of the
$\ev_{!_0} \vdash \ext$ adjunction --- which is the universal cell defining the
right Kan extension --- is an equivalence by Proposition 9.4.4 of \cite{RV:Elements}. 
\end{proof}

\begin{prop}\label{prop:set.characterizing.extent}
  Let $\pi : E \to B$ be a bundle. The following are equivalent:
  \begin{enumerate}
  \item The extent $\ext_{\pi} : \Ha\op \to \Ha$ of $\pi$.
  \item The functor
    $$S \mapsto \sum_{b : B} E_b^S,$$
    or equivalently the composite
  $$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
  \xto{B_{\ast}} \Ha.$$
\item The restricted representable functor
  $\Ha^{\down}(!_{(-)}, \pi)$.
\item The functor
  $$S \mapsto \lim(\Hom_{\Ha}(!_0, S) \to \down \xto{\pi} \Ha)$$
  where $\Hom_{\Ha}(!_0, S)$ is the slice category of $!_0 : \down \to
  \Ha$ over $S$.
\item The functor
  $$S \mapsto \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
  \xto{\pi} \Ha)$$
  where $(-)^{\triangleleft}$ is the \emph{left cone}.
  \end{enumerate}
\end{prop}
\begin{proof}
We have presented these results in order of most understandable to most
computational; we will prove it a somewhat opposite order.

First, we note that 
$$S \mapsto \lim(\Hom_{\Ha\op}(S, !_0) \to \down \xto{\pi} \Ha)$$
is the right Kan extension formula for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$ --- see Corollary 9.5.3 of \cite{RV:Elements}. Noting that $\Hom_{\Ha}(!_0, S) = \Hom_{\Ha\op}(S,
!_0)$, we see that (1) is equivalent to (4). Furthermore, noting that
$\Hom_{\Ha}(!_0, S)$ simply adjoins an initial object to (the discrete
category) $S$, we see that (4) is equivalent to (5).

Now, we note that every set $S$ is the colimit of the diagram $S^{\triangleleft}
\xto{\ast^{\triangleleft}} \xto{!_0} \Ha$. Since, by Lemma \ref{lem:bang.preserves.weakly.contractible.colimits}, $!_{(-)}$
preserves weakly contractible colimits, {\color{red} TODO}.

Finally, we calculate $\Ha^{\down}(!_{\ast}, \pi)$ homotopy type-theoretically:
\begin{align*}
\Ha^{\down}(!_{\ast}, \pi) &= \sum_{b : \ast \to B} \sum_{f : X \to E}
                                  (\pi \circ f = b \circ !_X)\\
                                &= \sum_{b : B} \sum_{f : X \to E} \prod_{x : X} (\pi (f x) = b) \\
                                &= \sum_{b : B} \left( X \to \sum_{e : E} (\pi e = b) \right) \\
                                  &\equiv \sum_{b : B}E_b^X.
\end{align*}
{\color{red} But I need a better argument to show that this is a natural
  equivalence of functors --- something involving cartesian fibrations etc etc etc}
\end{proof}

Now we are ready to intrinsically characterize the Dirichlet functors.
\begin{thm}
A functor $D : \Ha\op \to \Ha$ is Dirichlet if and only if it preserves
weakly contractible limits. 
\end{thm}
\begin{proof}
First, we show that Dirichlet functors preserve connected limits. If $D$ is
Dirichlet, then by Prop \ref{prop:set.characterizing.extent}, $D$ is naturally
equivalent to the composite
$$\Ha\op \xto{(B^{\ast})\op} (\Ha_{/B})\op \xto{[-, \pi]} \Ha_{/B}
\xto{B_\ast} \Ha.$$
As $(B^{\ast})\op$ is a right adjoint, it commutes with all limits, and as $[-,\pi]$
is part of a multivariable adjunction, it also commutes with all limits.
Finally, we note that $B_{\ast}$ commutes with weakly contractible limits by
Lemma 2.2.7 of \cite{GHK:Analytic.Monads}.

Now, we show that if $D$ commutes with weakly contractible limits, then the unit
$D \to \ext_{D!_0}$ is an equivalence. By Prop
\ref{prop:set.characterizing.extent}, 
  $$\ext_{D!_0}(S) = \lim(S^{\triangleleft} \xto{!^{\triangleleft}} \ast^{\triangleleft}
  \xto{D!_0} \Ha).$$

Every homotopy type $S$ is the weakly contractible colimit of the diagram $S^{\triangleleft} \to
\down \xto{!_0} \Ha$ because it is the colimit of the diagram $S \to \ast
\xto{\ast} \Ha$ and we are extending this diagram with an initial object (see
Lemma \ref{lem:extending.diagram.with.initial.object.has.same.colimit}). Therefore if $D$ preserves this limit, then
$D(S)$ is precisely the above limit $\ext_{D!_0}(S)$.
\end{proof}

Next, we turn to cartesian morphisms.
\begin{prop}\label{prop:type.dirichlet.cartesian.iff.bundle.cartesian}
A natural transformation $\phi : D \to D'$ between Dirichlet functors is
cartesian if and only if the induced bundle map $D!_0 \to D'!_0$ is a pullback.

As a corllary, the equivalence $\Dir \simeq \Ha^{\down}$ restricts to an
equivalence
$$\Dir_{\ulcorner} \simeq \Ha^{\down}_{\ulcorner}$$
between Dirichlet functors and cartesian natural transformations and bundles and
pullback sqaures.
\end{prop}
\begin{proof}
We want to show that for any $f\colon D\to D'$ the square
\begin{equation}\label{eqn.type.cart1}
\begin{tikzcd}
	D(1)\ar[r, "f_1"]\ar[d, "\pi"']&
	D'(1)\ar[d, "\pi'"]\\
	D(0)\ar[r, "f_0"']&
	D'(0)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$ iff for all functions $g\colon X\to X'$, the naturality square
\begin{equation}\label{eqn.type.cart2}
\begin{tikzcd}
  D(X')\ar[r, "f_{X'}"]\ar[d, "D(g)"']&
  D'(X')\ar[d, "D'(g)"]\\
  D(X)\ar[r, "f_X"']&
  D'(X)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$. We will freely use the natural isomorphism
$D(X)\cong\Set^{\down}(!_X, D!_0)$ from
\ref{prop:set.characterizing.extent}, which allows us to identify Diagram
\ref{eqn.type.cart2} with
\begin{equation}\label{eqn.cart3}
\begin{tikzcd}
 \Set^{\down}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Set^{\down}(!_{X'}, D'!_0)
  \ar[d, "!_{g}^{\ast}"]\\
  \Set^{\down}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
 \Set^{\down}(!_X, D'!_0) 
\end{tikzcd}
\end{equation}

The square in Diagram \ref{eqn.type.cart1} is a
special case of that in Diagram \ref{eqn.type.cart2}, namely for $g\coloneqq !_0$;
this establishes the only-if direction.

To complete the proof, suppose that Diagram \ref{eqn.type.cart1} is a pullback, take an arbitrary $g\colon X\to X'$, and suppose given a commutative solid-arrow diagram as shown:
\[
\begin{tikzcd}[sep=small]
  X\ar[rr, "g"]\ar[dd]\ar[rd]&&
  X'\ar[dr]\ar[dd]\ar[dl, dotted]\\&
  D(1)\ar[rr, crossing over]&&
  D'(1)\ar[dd]\\
  1\ar[dr]\ar[rr, equal]&&
  1\ar[dr]\ar[dl, dotted]\\&
  D(0)\ar[from=uu, crossing over]\ar[rr]&&
  D'(0)
\end{tikzcd}
\]
We can interpret the statement that Diagram \ref{eqn.type.cart3} is a pullback as
saying that there are unique dotted arrows making the diagram commute. So, we
need to show that if the front face is a pullback, then there are unique
diagonal dotted arrows as shown in the homotopy type-theoretical sense.
{\color{red} TODO} 
\end{proof}

\begin{thm}\label{thm:type.poly.cart.equiv.dir.cart}
  There is an equivalence of $\infty$-categories
  $$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
  between the category of polynomial functors and cartesian transformations and
  Dirichlet functors and cartesian transformations. This equivlalence sends
  representables to representables
  $$(-)^N \mapsto N^{(-)}.$$
\end{thm}
\begin{proof}
This follows by composing the equivalence of $\Dir_{\ulcorner}$ with
$\Ha^{\down}$ from Prop
\ref{prop:type.dirichlet.cartesian.iff.bundle.cartesian} with that of
Proposition 2.4.13 of \cite{GHK:Analytic.Monads}, noting that
$\Ha^{\down}_{\ulcorner}$ is the category of $(\ast,\ast)$-polynomials. 
\end{proof}

\begin{cor}
  Let $D$ be a Dirichlet functor. Then the $\infty$-category
  $\Dir_{/_{\ulcorner} D}$
  of Dirichlet functors with a cartesian map to $D$ is an $\infty$-topos.
\end{cor}
\begin{proof}
By Theorem \ref{thm:type.poly.cart.equiv.dir.cart}, this $\infty$-category is equivalent
to $\type{Poly}_{/_{\ulcorner} P}$ for a polynomial $P$. But this is an
$\infty$-topos by Theorem 2.6.1 of \cite{GHK:Analytic.Monads}.
\end{proof}

\section{Ordinary Dirichlet Functors} \label{sec:ordinary.dirichlet.functors}

In this section, we will categorify Dirichlet series
$$\sum_{n \in \Nb} a_n n^{-s}.$$

First, we review the notion of \emph{homotopy cardinality}.

\begin{defn}
Let $B$ be a homotopy type. We define the \emph{homotopy cardinality} $\#B$ to be
the following sum:
$$\#B := \sum_{[b] \in \pi_0(B)} \prod_{n = 1}^{\infty} |\pi_n(B, b)|^{(-1)^n}$$

We note that
$$\#B = \sum_{[b] \in \pi_0(B)} \frac{1}{\#\Omega(B, b)}$$
\end{defn}

We will leave questions concerning the convergence and well-definedness of the
homotopy cardinality of a type, noting only that if a type $B$ is totally finite in
that it has finitely many connected components, its homotopy groups are finite,
and they eventually vanish, then $\#B$ is a finite sum of a finite product and so
is well defined.

The main lemma concerning homotopy cardinality is its behavior with respect to
fibrations.
\begin{lem}
Let $\pi : E \to B$ be a map of homotopy types, and let $E_b$ denote the fiber
over $b : B$. Then
$$\#E = \sum_{[b] \in \pi_0(B)}\frac{\#E_b}{\#\Omega(B, b)}.$$
As a corollary:
\begin{enumerate}
\item $\#(A \times B) = \#A \cdot \#B$ and so $\#(B^n) = (\#B)^n$.
\item If $B$ is pointed and connected and $F$ is the fiber of $\pi$ over the
  basepoint, then $\#E = \#F \cdot \#B$.
\item If $A_n$ is a family of types for $n : \Nb$, then $\#(\sum_n A_n) = \sum_n \#A_n$.
\end{enumerate}
\end{lem}
\begin{proof}
  We note that by the long exact sequence of homotopy groups, we have that
  $$|\pi_n(E, e)| = |\pi_n(E_{\pi e}, e)|\cdot |\pi_n(B, \pi e)|$$
  Therefore, we may calculate
  \begin{align*}
    \#E &= \sum_{[e] \in \pi_0(E)}\prod_{n=1}^{\infty} |\pi_n(E, e)|^{(-1)^n}\\
    &= \sum_{[b] \in \pi_0(B)} \sum_{[e] \in \pi_0(E_b)} \prod_{n=1}^{\infty} (|\pi_n(E_{b}, e)|\cdot |\pi_n(B, b)|)^{(-1)^n}\\
    &= \sum_{[b] \in \pi_0(B)}\prod_{n=1}^{\infty} |\pi_n(B, b)|^{(-1)^n} \sum_{[e] \in \pi_0(E_b)} \prod_{n=1}^{\infty} |\pi_n(E_{b}, e)|^{(-1)^n}\\
    &= \sum_{[b] \in \pi_0(B)}\frac{\#E_b}{\#\Omega(B, b)}.
  \end{align*}

  We may then take various maps $\pi : E \to B$ to recover the corollaries:
  \begin{enumerate}
  \item Take the projection $A \times B \to B$.
  \item Take the map $\pi : E \to B$, noting that if $B$ is pointed connected then $\#B =
    \frac{1}{\Omega B}$.
  \item Take the projection $\sum_n A_n \to \Nb$.
  \end{enumerate}
\end{proof}

Now, we note that if $B$ is connected, then $\#B = \frac{1}{\#\Omega(B, b)}$ for
any point $b : B$. Therefore, if $B$ is connected with finite homs of
cardinality $n$, then $\#B = \frac{1}{n}$ and so $\#(B^s) = n^{-s}$. This is the
observation --- originally due to Baez and Dolan in \emph{This Weeks Finds}
(cite) --- that we will use to categorify Dirichlet series.

\begin{defn}
A homotopy type $B$ is \emph{locally finite and connected}, or \emph{lfc}, if it
is $0$-connected and its homs are finite.

We denote by $\type{lfc}$ the homotopy type of lfc types, and note that the
bundle $\fst : \type{lfc}_{\ast} \to \type{lfc}$ forgetting the point of a
pointed lfc type classifies maps with lfc fibers.
\end{defn}

\section{Appendix}

\begin{lem}\label{lem:cone.initial.equivalence}
Let $\Ca$ be an $\infty$-category with an initial object. For any simplicial set
$J$, let $\Ca^{J^{\triangleleft}}_{\ast}$ be the $\infty$-category of
  $J^{\triangleleft}$-shaped diagrams whose apex is at the initial object; that
  is, the following pullback:
  \[
    \begin{tikzcd}
      \Ca^{J} \arrow[drr, bend left] \arrow[ddr, bend right] \arrow[dr,
      dotted, "\sim"] & & \\
      & \Ca^{J^{\triangleleft}}_{\ast} \arrow[d] \arrow[r] \arrow[dr, phantom,
      "\ulcorner" very near start] & \Ca^{J^{\triangleleft}} \arrow[d,
      "\term{ev}_{\term{apex}}"] \\
      & \ast \arrow[r, "0"'] & \Ca
    \end{tikzcd}
  \]
The the dotted extension map  $\epsilon : \Ca^{J} \to \Ca^{J^{\triangleleft}}_{\ast}$ is an equivalence.
\end{lem}

\begin{lem}\label{lem:kan.extending.cone.adds.initial}
If $\Ca$ is an $\infty$-category with an initial object, then the restriction
$\Ca^{J^{\triangleleft}} \to \Ca^{J}$ has a left adjoint right inverse $\epsilon
: \Ca^J \to \Ca^{J^{\triangleleft}}$ extending a diagram by adjoining the
initial object. 
\end{lem}
\begin{proof}

\end{proof}

\begin{lem}\label{lem:extending.diagram.with.initial.object.has.same.colimit}
If $\Ca$ is an $\infty$-category with an initial object $0$, and $d : D \to
\Ca^J$ a family of diagrams with colimit $\colim d : D \to \Ca$, then the family
$D \xto{d} \Ca^J \xto{\epsilon} \Ca^{J^{\triangleleft}}$ has colimit $\colim d$.
\end{lem}
\begin{proof}
For $\colim d : D \to \Ca$ to be the colimit of $d : D \to \Ca^J$ means that 
\end{proof}

>>>>

We want to show that for any $f\colon D\to D'$ the square
\begin{equation}\label{eqn.cart1}
\begin{tikzcd}
	D(1)\ar[r, "f_1"]\ar[d, "\pi"']&
	D'(1)\ar[d, "\pi'"]\\
	D(0)\ar[r, "f_0"']&
	D'(0)
\end{tikzcd}
\end{equation}
is a pullback in $\Ha$ iff for all functions $g\colon X\to X'$, the naturality square
\begin{equation}\label{eqn.cart2}
\begin{tikzcd}
  D(X')\ar[r, "f_{X'}"]\ar[d, "D(g)"']&
  D'(X')\ar[d, "D'(g)"]\\
  D(X)\ar[r, "f_X"']&
  D'(X)
\end{tikzcd}
\end{equation}
is a pullback in $\Set$. We will freely use the natural isomorphism
$D(X)\cong\Set^{\down}(!_X, D!_0)$ from
\ref{prop:set.characterizing.extent}, which allows us to identify Diagram
\ref{eqn.cart2} with
\begin{equation}\label{eqn.cart3}
\begin{tikzcd}
 \Set^{\down}(!_{X'}, D!_0)     \ar[r, "f_{!_0,\ast}"]\ar[d, "!_g^{\ast}"']& \Set^{\down}(!_{X'}, D'!_0)
  \ar[d, "!_{g}^{\ast}"]\\
  \Set^{\down}(!_{X}, D!_0)\ar[r, "f_{!_0, \ast}"']&
 \Set^{\down}(!_X, D'!_0) 
\end{tikzcd}
\end{equation}

@@

\begin{thm}\label{thm:set.poly.cart.equiv.dir.cart}
  There is an equivalence of categories
  $$\type{Poly}_{\ulcorner} \simeq \Dir_{\ulcorner}$$
  between the category of polynomial functors and cartesian transformations and
  Dirichlet functors and cartesian transformations. This equivlalence sends
  representables to representables
  $$(-)^N \mapsto N^{(-)}.$$
\end{thm}
\begin{proof}
  \jaz{Need to find a good citation for this result --- that polynomial functors
  and cartesian transforms are bundles and cartesian maps (for 1-cats).}
\end{proof}

\begin{cor}
  Let $D$ be a Dirichlet functor. Then the category
  $\Dir_{/_{\ulcorner} D}$
  of Dirichlet functors with a cartesian map to $D$ is a topos.
\end{cor}
\begin{proof}
By Theorem \ref{thm:set.poly.cart.equiv.dir.cart}, this category is equivalent
to $\type{Poly}_{/_{\ulcorner} P}$ for a polynomial $P$. But this is a topos as
observed in Remark 2.6.2 of \cite{GHK:Analytic.Monads}.
\end{proof}
\dis{How does this topos compare to the topos $\Dir_{/D}$?}
\jaz{See the $\infty$-categorical case. The same story can be told for
  1-categories, but perhaps we should tell it some other way?}
